\documentclass[10pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')


% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

\usepackage{url}
\usepackage{uri}
\usepackage[abbreviations=false]{siunitx}
\sisetup{%
  retain-unity-mantissa = false,% avoid 1 x 10^{4}
  range-units = single,% do not repeat units, e.g.: 2,3 and 4 T
  range-phrase = --% 
}

\usepackage{amssymb}
\usepackage{amsmath}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths{}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Jes\'{u}s Misr\'{a}yim}{Rueda-Becerril}
\title{PhD candidate}                             % optional, remove / comment the line if not wanted
\address{Av. Paseo Rajolar 2, Piso 7}{46100, Burjassot}{Valencia, SPAIN}  % optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+34~61~572~8749}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
%\phone[fixed]{}
%\phone[fax]{}
\email{jesus.rueda@uv.es}
%\homepage{}                         % optional, remove / comment the line if not wanted
\social[linkedin]{Jesus Rueda-Becerril}          % optional, remove / comment the line if not wanted
%\social[twitter]{jerue103}                             % optional, remove / comment the line if not wanted
\social[github]{altjerue}                              % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{}                                 % optional, remove / comment the line if not wanted

%% -------------------------------  BIBLIOGRAPHY  --------------------------

%    bibliography with mutiple entries
\usepackage{multibib}
\newcites{jour,conf}{{Articles}, {Proceedings}}
\usepackage[numbers]{natbib}

%    to redefine the bibliography heading string ("Publications")
% \renewcommand{\refname}{Articles}

%    this produces the bibliography to be numbered decreasingly, fully
%    compatible with natbib and multibib
\newlength{\lmar}
\setlength{\lmar}{\hintscolumnwidth}
\addtolength{\lmar}{\separatorcolumnwidth}
\usepackage[topsep=0pt,leftmargin=\lmar]{etaremune}
\usepackage{etoolbox}
\makeatletter
\AtBeginDocument{%%% natbib redefines the environment there
  \renewenvironment{thebibliography}[1]
  {%
    \bibliographyhead{\refname}%
    \begin{etaremune}
      \@openbib@code%
      \sloppy%
      \clubpenalty4000%
      \widowpenalty4000%
      \sfcode`\.\@m%
      \sfcode`\=1000\relax}%
    {\bibitem@fin\bibpostamble%
      \def\@noitemerr{\latex@warning{Empty `thebibliography' environment}}%
    \end{etaremune}
    \bibcleanup}
}%%% end of \AtBeginDocument
%%% patch \@lbibitem to use only \item (for etaremune)
\patchcmd{\@lbibitem}{\item[\hfil\NAT@anchor{#2}{\NAT@num}]}{\item}{}{}
\makeatother

%%--------------------------------------------------------------------------
%% New macros
\newcommand{\mbs}{Mag\-ne\-to\-brems\-strah\-lung}

\newcommand{\UVval}{Universitat de Val\`{e}ncia}
\newcommand{\UVes}{Universidad de Valencia}
\newcommand{\UVen}{University of Valencia}
\newcommand{\DAAval}{Departament d'Astronomia i Astrof\'{\i}sica}
\newcommand{\DAAes}{Departamentento de Astronom\'{\i}a y Astrof\'{\i}sica}
\newcommand{\DAAen}{Department of Astronomy and Astrophysics}
\newcommand{\IFMes}{Instituto de F\'{\i}sica y Matem\'{a}ticas}
\newcommand{\IFMen}{Institute of Physics and Mathematics}
\newcommand{\UMSNHes}{Universidad Michoacana de San Nicol\'{a}s de Hidalgo}
\newcommand{\UMSNHen}{Michoacan University of Saint Nicholas of Hidalgo}
\newcommand{\UAEMex}{UAEM\'{e}x}
\newcommand{\UAEMes}{Universidad Aut\'{o}noma del Estado de M\'{e}xico}
\newcommand{\UAEMen}{Autonomous University of the State of Mexico}

\newcommand{\prd}{Phys. Rev. D}
\newcommand{\mnras}{Mon. Not. R. Astron. Soc.}

%---------------------------------------------------------------------------
%            content
%---------------------------------------------------------------------------
%

\begin{document}

% ---------------------------   resume   -----------------------------------
\makecvtitle%

\section{Education}

\cventry{2011--}{PhD in Physics}{\UVval}{Valencia, Spain}{}{Supervisors:
  Prof.\ Miguel\ \'{A}ngel Aloy Tor\'{a}s and Dr.\ Petar\ Mimica \newline%
  Thesis: \textit{Radiation Transport in Relativistic Magnetized Fluids ---
    Applications to Relativistic Outflows}}
%
\cventry{2009--2011}{MSc in Physics}{\IFMes, \UMSNHes}{Morelia,
  Michoacan, Mexico}{}{Supervisor: Prof.\ Jos\'{e} Antonio Gonz\'{a}lez
  Cervera \newline%
  Thesis: \textit{Study of TOV stars with the SPH method}}
%
\cventry{2004--2009}{BSc in Physics}{\UAEMes}{Toluca, State of
  Mexico, Mexico}{}{Supervisor: Prof.\ Francisco S. Guzm\'{a}n Murillo
  \newline%
  Thesis: \textit{Numerical solution of null geodesics for the generation
    of gravitational lenses in spherically symmetric space-times}}
% arguments 3 to 6 can be left empty


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Computer skills}

\cvitem{Proficient}{Unix (Linux, macOS), FORTRAN (77, 90, 95, 2003),
  Python, Shell, Mathematica, \LaTeX, gnuplot, grace, OpenMP, GeoGebra,
  Emacs, HDF5, Makefile, Git}
%
\cvitem{Intermediate}{C, C++, R, Julia, Elisp, MPI, SageMath, yEd,
  OpenOffice, Microsoft Office, iWork, DOT, TikZ/PGF}
%
\cvitem{Basic}{HTML, Matlab, Maple, Java, Swift, Perl}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  PUBLICATIONS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Publications}           % ----- multibib -----
%%\nocitebook{book1,book2}
%%\bibliographystylebook{plain}
%%\bibliographybook{publications}         % 'publications' is the name of a BibTeX file

\nocitejour{Rueda:2017hd,Rueda:2014mn,Guzman:2009bk}
\nociteconf{Rueda:2014sw,Rueda:2013ep,Mimica:2013iu}
\bibliographystylejour{unsrt}
\bibliographystyleconf{unsrt}
\bibliographyjour{/Users/jesus/RemoteRepos/GitHub/jmrb_cv/MyPapers.bib}
\bibliographyconf{/Users/jesus/RemoteRepos/GitHub/jmrb_cv/MyPapers.bib}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% \section{PhD thesis}
% \cvitem{title}{\textit{}}
% \cvitem{supervisors}{Prof. Miguel A. Aloy\\ Dr. Petar Mimica}
% \cvitem{description}{Short thesis abstract}
%
% \section{MSc thesis}
% \cvitem{title}{\textit{}}
% \cvitem{supervisors}{Prof. Jose A. Gonz\'{a}lez}
% \cvitem{description}{Short thesis abstract}
%
%\section{Bachelors thesis}
%\cvitem{title}{\textit{}}
%\cvitem{supervisor}{Prof. Francisco S. Guzm\'{a}n}
%\cvitem{description}{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\clearpage%
\section{Interests}

\cvitem{High energy physics around black holes}{
  \begin{itemize}
  \item Theory and observation of high energy radiation in different
    scenarios where black holes are involved.
    \begin{itemize}
    \item Radiation transport.
    \item Radiation source and source region.
    \item Particles acceleration processes.
    \end{itemize}
  \item Active galactic nuclei.
    \begin{itemize}
    \item Blazars.
      \begin{itemize}
      \item Acceleration processes in the emission region.
      \item Location of the emission region.
      \item The spectral effects due to different constituents of the
        material in the emission region.
      \end{itemize}
    \item Radio galaxies.
    \item Quasars.
    \end{itemize}
  \item Tidal disruption events.
  \item Microquasars.
  \item Gamma-ray bursts.
  \end{itemize}
}
%
\cvitem{Numerical Astrophysics}{
  \begin{itemize}
  \item Numerical solutions to the radiation transport equation with
    astrophysical applications.
  \item Numerical treatment of the microphysics involved in the emission
    of high energy radiation.
  \item Numerical hydrodynamics and magnetohydrodynamics
  \item Performance, stability, convergence and accuracy of numerical
    codes.
  \end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% \subsection{Teaching}
% \cventry{year--year}{}{}{}{}{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Meetings and conferences}

\subsection{Oral presentations}

\cventry{2014}{Rueda-Becerril, J.M.\textnormal{; Mimica, P.; Aloy,
    M.A.}}{Numerical simulations of the internal shock model in
  magnetized relativistic jets of blazars}{IVICFA's Fridays: Computation
  in Physics}{Paterna, Spain, 17 October}{}
%
\cventry{2014}{Rueda-Becerril, J.M.\textnormal{; Mimica, P.; Aloy,
    M.A.}}{Influence of the magnetic field on the spectral properties of
  blazars in the internal shocks scenario}{Extreme-Astrophysics in an
  Ever-Changing Universe: Time-Domain Astronomy in the 21st
  Century}{Ier\'{a}petra, Greece, 16--20 June}{}
%
\cventry{2013}{Rueda-Becerril, J.M.\textnormal{; Mimica, P.; Aloy,
    M.A.}}{Numerical study of broadband spectra caused by internal shocks
  in magnetized relativistic jets}{XXXIV Biennial meeting of the Royal
  Spanish Society of Physics}{Valencia, Spain, 15--19 July}{}
%
\cventry{2009}{Rueda-Becerril, J.M}{\textquestiondown{}Dec\'{\i}a Einstein
  la verdad?}{weekly colloquium of Physics students \emph{Caf\'{e}
    Ciencias}}{Toluca, Mexico, 11 March}{}

\subsection{Poster presentations}

\cventry{2014}{Rueda-Becerril, J.M.\textnormal{; Mimica, P.; Aloy,
    M.A.}}{Numerical simulations of the internal shock model in
  magnetized relativistic jets of blazars}{Swift: 10 years of
  Discovery}{Rome, Italy, 2--5 December}{}
%
\cventry{2013}{Rueda-Becerril, J.M.\textnormal{; Mimica, P.; Aloy,
    M.A.}}{Numerical study of broadband spectra caused by internal shocks
  in magnetized relativistic jets of blazars}{The Innermost Regions of
  Relativistic Jets and Their Magnetic Fields}{Granada, Spain, 10--14 June}{}
%
\cventry{2007}{Rueda-Becerril, J.M.\textnormal{; Leyte Gonz\'{a}lez, R.;
    Garc\'{\i}a Santiba\~{n}ez, F.; Rosendo-Francisco, P.}}{Analysis of
  the superficial structure of graphite samples submitted to an electric
  arc}{L National Physics Meeting}{Boca del R\'{\i}o, Mexico, 29
  October--2 November}{}
%
\cventry{2006}{Rueda-Becerril, J.M.\textnormal{; Leyte Gonz\'{a}lez, R.;
    Garc\'{\i}a Molina, N.; Rosendo-Francisco, P.}}{Modifications on the
  superficial structure of graphite samples}{XLIX National Physics
  Meeting}{San Luis Potos\'{\i}, Mexico, 16--19 October}{}
%
\cventry{2005}{Rueda-Becerril, J.M.\textnormal{; G\'{o}mez D\'{\i}az, A.;
    Rosendo-Francisco, P.}}{Studies of microwave effects of graphite
  samples}{XLVIII National Physics Meeting}{Guadalajara, Mexico, 17--21
  October}{}

\subsection{Attendance only}

\cvitem{2016}{CoCoNuT Meeting 2016, Burjassot, Spain, 14--16 December}
%
\cvitem{2008}{LI National Physics Meeting, Zacatecas, Mexico, 20--24
  October}

\subsection{Organization}

\cvitem{2012}{Contribution to the organization of the X Scientific Meeting
  of the Spanish Astronomical Society, Valencia, Spain, 14--16 December}


\section{Professional development}

\cventry{7--16 Feb 2017}{Data Analysis and Machine Learning with
  Python}{UV}{Burjassot}{Spain}{No.\ of hours: 8}
%
\cventry{23--16 May 2014}{The Universe in the light of PLANCK and
  BICEP2}{UV}{Burjassot}{Spain}{No.\ of credits: 2}
%
\cventry{23--27 Sep 2013}{Dark Matter}{UV}{Burjassot}{Spain}{No.\ of
  credits: 2}
%
\cventry{23 Apr--8 May 2013}{International Cag\`{e}se School on Cosmic
  Accelerators}{Institut d'\'{E}tudes Scientifques de
  Carg\`{e}se}{Carg\`{e}se}{France}{}
%
\cventry{9--12 Apr 2012}{Introduction to C++
  Programming}{UV}{Burjassot}{Spain}{No.\ of credits: 6}
%
\cventry{27 Mar--4 Apr 2012}{Numerical Relativistic
  Astrophysics}{UV}{Burjassot}{Spain}{No.\ of hours: 9}
%
\cventry{5--9 March 2012}{Fortran for Scientific Computing}{High
  Performance Computing Center Sttutgart}{Stuttgart}{Germany}{No.\ of
  hours: 33}
%
% \cventry{Jun 2006}{Advanced Summer School}{CINVESTAV}{Ciudad de
%   M\'{e}xico}{Mexico}{}
% %
% \cventry{Aug 2006}{Advanced Summer School}{Instituto de F\'{\i}sica of the
%   Universidad de Guanajuato}{Le\'{o}n}{Mexico}{}


\section{Awards and Scholarships}

\cvitem{2014--2016}{\textbf{Fellowship} from the Mexican Federal Government
  to study abroad awarded by the National Council of Science and Technology
  (CONACyT).}
% 
\cvitem{2011--2014}{ \textbf{Fellowship} ``Santiago Grisol\'{\i}a'' awarded
  by the Council of Education, Research, Culture and Sport of the Valencian
  Comunity.}
%
\cvitem{2009--2011}{\textbf{Fellowship} for academic training for MSc
  studies granted by the Mexican Council of Science and Technology
  (CONACyT).}
%
\cvitem{2009}{\textbf{Award} ``Lic. Juan Josafat Pichardo Cruz'', granted
  by the \UAEMex, for finishing the BSc thesis and graduating within a year
  after completing the undergraduate credits.}
%
\cvitem{25 Jun--24 Aug 2007}{\textbf{Fellowship} for a temporary stay in a
  national research center under the XVII summer of scientific
  investigation program awarded by the Mexican Academia of Science.}


\section{Other activities}
\cvitem{2007--2009}{Physics students representative at the
  Governing Council of the Faculty of Sciences of the \UAEMex}{}{}{}{}


\section{Languages}

% \cvitemwithcomment{Language 3}{Skill level}{Comment}
\cvitemwithcomment{Spanish}{Mother tongue}{}
\cvitemwithcomment{English}{Proficient}{}
\cvitemwithcomment{Catalan}{Basic}{}%IELTS and TOEFL certified.}
\cvitemwithcomment{French}{Basic}{}%IELTS and TOEFL certified.}
\cvitemwithcomment{German}{Basic}{}%IELTS and TOEFL certified.}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}

%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{Biblio}                        % 'publications' is the name of a BibTeX file


%\clearpage
% ---------------------       letter       ---------------------------------
%       recipient data
% \recipient{Department of }{University Address}
% \date{\today}
% \opening{Dear RECIPIENT,}
% \closing{Best regards,}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
% %
% \makelettertitle%
% %

% \makeletterclosing%

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
