%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Grants}

\cventry{2019}%
{A simple model to understand the blazar sequence}%
{NASA Fermi Cycle-12 Guest Investigator Program}%
{Grant \#121077}%
{}%
{PI: Giannios, D., Co-I: \textbf{Rueda-Becerril, J.~M.}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grants and Fellowships}

\cvitem{2018 -- 2020}{\textbf{Fellowship} from the Mexican Federal Government for a postdoctoral stay abroad awarded by the National Council of Science and Technology (CONACyT).}
%
\cvitem{2018}{\textbf{Fellowship} from the Mexican Federal Government under the \emph{Program for the Professional Development of Higher Education Institutions}, awarded by the Secretariat of Public Education.}
%
\cvitem{2014 -- 2016}{\textbf{Fellowship} from the Mexican Federal Government to study abroad awarded by the National Council of Science and Technology (CONACyT).}
%
\cvitem{Oct. 2011 -- Jun. 2014}{\textbf{Fellowship} \textit{Santiago Grisol\'{\i}a} awarded by the Council of Education, Research, Culture and Sport of the Valencian Comunity, Spain.}
%
\cvitem{Sep. 2009 -- Aug. 2011}{\textbf{Fellowship} for MSc studies at the \IFMen, \UMSNHes, granted by the Mexican Council of Science and Technology (CONACyT).}
%
\cvitem{Jun. -- Aug. 2007}{\textbf{Fellowship} for a temporary stay (3 months) in a national research center under the \emph{XVII summer of scientific investigation program} awarded by the Mexican Academia of Science.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards}

\cvitem{2009}{\textbf{Award} \textit{Lic. Juan Josafat Pichardo Cruz}, granted by the \UAEMen, for finishing and defending a thesis within a year after completing the undergraduate credits.}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
