\section{Experience}
%--------------------
\cventry{}%
{Independent Contractor}%
{Mercor}%
{Jan 2026 — Present}%
{}%
{%
\begin{itemize}
  \item Providing deep expertise in Physics and numerical methods to improve
  LLM models for a top AI lab.
\end{itemize}
}
%--------------------
\cventry{}%
{Spatial Data Scientist}%
{TealWaters}%
{May 2025 — Jan 2026}%
{}%
{%
\begin{itemize}
  \item Processed multispectral satellite imagery (Sentinel-1/2) for land-cover
  classification; built geospatial data pipelines for ML/AI applications using
  Python and QGIS.
  \item Applied random forest ML for wetland probability mapping; performed
  EDA, feature engineering, and geospatial data preparation for production ML
  models.
  \item Led optimization of scientific code for topographic terrain modeling,
  improving computational performance of elevation derivative calculations.
  \item Collaborated with software engineers to transition prototype simulation
  tools into production.
\end{itemize}
}
%--------------------
%\cventry{}%
%{\vspace{-10pt}}%
%{Independent Research/Open-Source Developer}%
%{Jan 2024 — May 2025}%
%{}%
%{%
%\begin{cvcolumns}
%  \cvcolumn{Tleco}{Combines Rust and Python functions from the Fortran code
%  \texttt{Paramo} to simulate relativistic plasma particles and radiation rise
%  from accelerating particles.}
%  \cvcolumn{WindsOfChange}{R package, written in C++ that simulates canopy
%  spore dispersion in hilly terrains.}
%\end{cvcolumns}\vspace{-15pt}
%}
%--------------------
\cventry{}%
{Postdoctoral Research Associate}%
{Rochester Institute of Technology}%
{Feb 2021 — Apr 2022}%
{}%
{%
\begin{itemize}
  \item Led NSF-sponsored upgrade of PatchworkMHD, a large-scale C-based HPC
  simulation code for supermassive black hole binaries, on the Frontera
  supercomputer (TACC); added physics features without impacting runtime.
  \item Applied scientific ML (gradient-based optimization) to calibrate
  physical model parameters against telescope observations, demonstrating
  ML-assisted simulation workflows for complex physical systems.
  \item Designed and ran large-scale computational experiments on Frontera;
  benchmarked and identified performance optimization opportunities in
  parallel HPC code.
  \item Collaborated on multi-institutional HPC simulation project studying
  binary neutron star mergers, resulting in 2 publications.
\end{itemize}
}
%-----------------------------------
\cventry{}%
{Postdoctoral Research Fellow}%
{\Purdue}%
{Oct 2018 -- Nov 2020}%
{}%
{%
\begin{itemize}
  \item Architected and developed Paramo, an open-source
  multiscale/multiphysics simulation library in Fortran 95 modeling
  relativistic particle distributions via the Fokker-Planck equation coupled
  with radiative transfer; achieved 60x runtime speedup via OpenMP
  parallelization; explored GPU acceleration via OpenACC.
  \item Implemented advanced numerical PDE solvers, numerical integration
  algorithms, and particle distribution methods with arbitrary shape support
  across temporal and spatial scales.
  \item Generated large synthetic datasets across a high-dimensional physical
  parameter space for model validation and parameter estimation workflows.
  \item Obtained and led a NASA grant (\$68K) to model radiation from active
  galaxies; managed 3 PhD researchers and published 2 peer-reviewed papers.
\end{itemize}
}
%-----------------------------------
\cventry{}%
{Postdoctoral Research Fellow}%
{\UMSNHes}%
{Jan -- Sep 2018}%
{}%
{%
\begin{itemize}
  \item Developed a Python pipeline to process black hole simulation outputs,
  generating SVM training data for radio image prediction.
  \item Built open-source data analysis and visualization tools in Python for
  radiative transfer phenomena in relativistic astrophysics scenarios.
\end{itemize}
}
%--------------------
\cventry{}%
{Software Engineer}%
{\PYX}%
{Apr 2022 — Jan 2024}%
{}%
{%
\begin{itemize}
  \item Developed Java Kafka consumers for high-throughput data transfer across
  enterprise databases; deployed to production via Jenkins and OpenShift using
  CI/CD pipelines.
  \item Conducted SQL data preparation, validation, and analysis from Oracle
  EBS datasets; built Splunk dashboards for production monitoring.
\end{itemize}
}
%-----------------------------------
\cventry{}%
{Graduate Research Assistant}%
{\UVval}%
{Oct 2011 -- Jul 2017}%
{}%
{%
\begin{itemize}
  \item Independently developed Shell and Python pipelines to run the C-SPEV
  radiative transfer simulation code and process large HDF5 output datasets.
  \item Implemented numerical tools and data handling extensions to C-SPEV for
  computing both discrete and continuous spectra from particle distributions
  with arbitrary shape.
  \item Published 2 first-author papers on numerical simulations of
  relativistic plasma dynamics.
\end{itemize}
}