%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional development}

%---------------------
\cventry{Lecture}%
{Dr. Lauren Broyles}%
{Writing Winning Grants}%
{}%
{\Purdue, West Lafayette, IN, USA, November 7, 2019}%
{}
%---------------------
\cventry{Workshop}%
{John Urbanic}%
{XSEDE HPC Workshop: Summer Boot Camp}%
{}%
{\Purdue, West Lafayette, IN, USA, June 3 -- 6, 2019}%
{}
%---------------------
\cventry{Workshop}%
{Dr. Alejandro Torres}%
{Data Analysis and Machine Learning with Python}%
{}%
{\UVval, Burjassot, Spain, February 7 -- 16, 2017}%
{}
%---------------------
\cventry{Workshop}%
{Dr. Vassilios Mewes}%
{Numerical relativity simulations of BBH coalescence using the Einstein Toolkit}%
{}%
{\UVval, Burjassot, Spain, July 6 -- 7, 2016}%
{No. of hours: 8}
%---------------------
\cventry{Lecture series}%
{Prof. Nick Mavromatos}%
{The Universe in the light of PLANCK and BICEP2}%
{}%
{\UVval, Burjassot, Spain, May 23 -- 16, 2014}%
{No. of credits: 2}
%---------------------
\cventry{Lecture series}%
{Dr. Alejandro Ibarra}%
{Dark Matter}%
{}%
{\UVval, Burjassot, Spain, September 23 -- 27, 2013}
{No. of credits: 2}
%---------------------
\cventry{Summer school}%
{Institut d'Études Scientifques de Cargèse}%
{International Cagèse School on Cosmic Accelerators}%
{}%
{Cargèse, France, April 23 -- May 8, 2013}%
{}
%---------------------
\cventry{Workshop}%
{Dr. Jacek Generowicz}%
{Introduction to C++ Programming}%
{}%
{\UVval, Burjassot, Spain, April 9 -- 12, 2012}%
{No. of credits: 6}
%---------------------
\cventry{Lecture series}%
{Prof. Luciano Rezzolla}%
{Numerical Relativistic Astrophysics}%
{}%
{\UVval, Burjassot, Spain, March 27 -- April 4, 2012}%
{No. of hours: 9}
%---------------------
\cventry{Workshop}%
{HLRS, University of Stuttgart}%
%{Dr. Uwe K\"{u}ster \& Dr. Ralf Schneider}%
{Fortran for Scientific Computing}%
{}%
{Stuttgart, Germany, Mar. 5 -- 9, 2012}%
{No. of hours: 33}
%---------------------
%\cventry{Summer school}%
%{CINVESTAV}%
%{Advanced Summer School}%
%{}%
%{Ciudad de México, Mexico, June 2006}%
%{}
%---------------------
%\cventry{Summer school}%
%{Instituto de Física}%
%{Advanced Summer School}%
%{}%
%{Universidad de Guanajuato, León, Mexico, August 2006}
%{}
%---------------------
