\section{Projects}
%—————————————————
\cventry{%
  \href{https://github.com/UW-ForestMycobiomeLab/WindSporesHills}{GitHub}}%
{WindsOfChange}%
{Open-Source Lagrangian Particle Simulation Library (R/C++)}%
{Aug 2024 — Present}%
{}%
{%
\begin{itemize}
  \item Developing C++ library implementing Lagrangian particle dispersion,
  atmospheric turbulence, and fluid flow over complex hilly terrains with
  forest canopy, based on analytical models (Massman \& Weil 1999; Finnigan
  \& Belcher 2004).
  \item Parallelized particle tracking using RcppParallel and OpenMP; designed
  for scalability to tens of thousands of particles across kilometer-scale
  domains.
\end{itemize}
}
%—————————————————
\cventry{}%
{PatchworkMHD}%
{Large-Scale MHD Simulation Code (NSF Project)}%
{Feb 2021 — Apr 2022}%
{}%
{%
\begin{itemize}
  \item Led upgrade of production C-based MHD simulation code for HPC
  environments; added physics features while maintaining performance at
  Frontera supercomputer scale.
\end{itemize}
}
%—————————————————
\cventry{\href{https://github.com/zkdavis/Tleco}{GitHub}}%
{Tleco}%
{Open-Source Physics Simulation Library (Python/Rust)}%
{Jan 2024 — Sep 2024}%
{}%
{%
\begin{itemize}
  \item Multiscale/multiphysics simulation toolkit combining Rust and Python
  interfaces for modeling relativistic particle distributions via Fokker-Planck
  equations coupled with radiative transfer.
  \item Implements numerical PDE solvers, particle distribution algorithms, and
  spectral calculation methods for relativistic plasma physics.
\end{itemize}
}
%—————————————————
\cventry{\href{https://github.com/altjerue/ilwikak-ml}{GitHub}}%
{Blazar Population ML}%
{Scientific ML (Python, scikit-learn, PyTorch)}%
{Jan 2026 — Present}%
{}%
{%
\begin{itemize}
  \item Applying classical ML and Bayesian inference to the Fermi-LAT 4LAC-DR3
  catalog (3,407 sources) to recover physical jet parameters from
  multi-wavelength observational data.
  \item Build a neural network to learn the mapping from physical jet
  parameters to observable SEDs accurately enough to compare with Tleco
  results.
  \item Forecast blazar gamma-ray flares using a general-purpose time series
  foundation model, fine-tuned with Tleco-generated synthetic light curves. 
\end{itemize}
}
%—————————————————
\cventry{\href{https://github.com/altjerue/paramo}{GitHub}}%
{Paramo}%
{Open-Source Physics Simulation Code (CONAHCYT Funded)}%
{Oct 2018 — Apr 2022}%
{}%
{%
\begin{itemize}
  \item Modular physics simulation library (Fortran 95 + OpenMP) modeling
  relativistic particle radiation; predecessor to Tleco.
\end{itemize}
}
%%—————————————————
%\cventry{\href{https://mexiciencia.github.io}{Homepage}}%
%{Group of Mexican Scientists bridging science and public knowledge}%
%{Co-Founder, Mexican Scientists Abroad}%
%{Aug 2019 — Feb 2021}%
%{}%
%{%
%\begin{itemize}
%  \item Collaborated on Python scripts for
%  \href{https://mexiciencia.github.io/post/covid19/}{COVID-19 modeling and
%  forecasting} in Mexico.
%  \item Authored
%  \href{https://mexiciencia.github.io/post/modelo-sir/}{blogposts} and
%  \href{https://mexiciencia.github.io/post/anita/}{infographics} to combat
%  misinformation.
%\end{itemize}
%}
